---
title: "Milestone 3"
author: "George Guarnieri"
date: "9/27/2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE,warning=FALSE,message=FALSE)
```



```{r}
library(tidyverse)
library(dplyr)
library(ggplot2)
library(readr)
library(janitor)

vend_data<-read.csv("vend-created_date-for-outlet.csv") %>%
  clean_names()
vend_data %>%
  group_by(supplier_code)%>%
  ggplot(aes(x=supplier_code,y=sell_through_rate)) +geom_col()+coord_flip()

```

For my final project plan, I hope to analyze data from The Harvard Shop. This semester, I will be taking over as the managing director of The Harvard Shop, and I have been granted access to all of the data from Vend (point of sale system) as well as Shopify (web sale system). My current plan for the final project is is to in some way utilize both of these datasets to draw conclusions that can help The Harvard Shop's procurement process. So far, to get started, I have started by reading in the data from Vend, and made a basic visual of sell through rates by vendor. 
