---
title: "Milestone 4"
author: "George Guarnieri"
date: "10/11/2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning=FALSE, message=FALSE)
```



```{r}
full_rawdata<-read.csv("sales_2016-10-18_2019-10-18.csv")
full_rawdata
```





```{r}

# Installed all necessary libraries

library(tidyverse)
library(dplyr)
library(ggplot2)
library(lubridate)
library(zoo)
library(gganimate)
library(png)

# Made a directory for graphics
dir.create('graphics')
# Read in the CSV file containing the data
vend_data_2_years<-read_csv("Milestone-6/vend-total_revenue-for-product-by-month (2).csv")

# Created a plot of Web Revenue by year.

vend_1<-vend_data_2_years%>%

# Arranged the data by descending revenue value. Selected the top 10 products in terms of Revenue. 
  
  arrange(desc(Revenue))%>%
  head(10)%>%
  
# Used the gather function to tame the data with key value pairs.
  
  gather(key="Month/Year", value="Revenue", `Nov 2017`:`Oct 2019`)%>%
  
# Selected the relevant variables
  
  select(Product, 'Month/Year', Revenue)%>%
  
# Extracted the years and grouped by product and year
  
  separate('Month/Year',c("Month","Year"))%>%
  group_by(Product,Year)%>%
  
# Summarized the sum of the revenue by product and year
  
  summarize(revenue=sum(Revenue))

# Created a plot showing revenue by product by year. Used a column chart and facet wrapped by year. Gave the chart a title, subtitle, and axis labels. Removed the tick labels from the x-axis since they were too crowded.
  

plot<-ggplot(vend_1,aes(x=Product,y=revenue,group=Product,fill=Product))+geom_col()+facet_wrap(~Year)+labs(title="Web Revenue by Product 2017-2019",subtitle="Data Sourced From Vend",y="Revenue",x="Product")+theme(axis.text.x=element_blank(),axis.ticks.x=element_blank())

saveRDS(plot,file='graphics/plot.rds')



                                                                          



```

In my plot, I decided to start examining Web Sales by product. Initially, I wanted to view this over time, but I realized that it would make more sense to facet the data since I was creating a column chart. While the data was already relatively clean, I ended up having to do more work than I had originally anticipated in order to make it work for the plot I had envisioned. The biggest step was remembering that I needed to use the gather function and then figuring out how to apply it in this case. After that, I also made sure I selected what I considered the most relevant products to be by arranging the data and selecting the top 10 products in terms of revenue. Lastly, I adjusted the aesthetics of the ploy as well in terms of the color, which pleased me aesthetically. 



```{r}
library(tidyverse)
#Customer counts
customer_counts<-read.csv("vend-customer_count-sales_summary-by-month.csv")

magic<-customer_counts%>%
   gather(key="Date", value="Customer_Count", X1.1.18:X10.1.19)%>%
    group_by(Date)
    
magic$generated_uid <- 1:nrow(magic)

magic%>%
  arrange(generated_uid)%>%
  ggplot(aes(x=Date,y=Customer_Count))+geom_point()

  
    
  
  
```

