---
title: "Milestone 4"
author: "George Guarnieri"
date: "10/11/2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning=FALSE, message=FALSE)
```



```{r}
# Read in data
full_rawdata<-read.csv("sales_2016-10-18_2019-10-18.csv")
```





```{r}

# Installed all necessary libraries

library(tidyverse)
library(dplyr)
library(ggplot2)
library(lubridate)
library(zoo)
library(gganimate)
library(png)
library(plotly)

# Made a directory for graphics

dir.create('graphics')

# Read in the CSV file containing the data.

vend_data_2_years<-read_csv("Milestone-6/vend-total_revenue-for-product-by-month (2).csv")

vend_data_2_years

# Created a plot of Web Revenue by year.

vend_1<-vend_data_2_years%>%

# Arranged the data by descending revenue value. Selected the top 10 products in terms of Revenue. 
  
  arrange(desc(Revenue))%>%
  head(10)%>%
  
# Used the gather function to tame the data with key value pairs.
  
  gather(key="Month/Year", value="Revenue", `Nov 2017`:`Oct 2019`)%>%
  
# Selected the relevant variables
  
  select(Product, 'Month/Year', Revenue)%>%
  
# Extracted the years and grouped by product and year
  
  separate('Month/Year',c("Month","Year"))%>%
  group_by(Product,Year)%>%
  
# Summarized the sum of the revenue by product and year
  
  summarize(revenue=sum(Revenue))

# Created a plot showing revenue by product by year. Used a column chart and facet wrapped by year. Gave the chart a title, subtitle, and axis labels. Removed the tick labels from the x-axis since they were too crowded.

plot<-ggplot(vend_1,aes(x=Product,y=revenue,group=Product,fill=Product))+geom_col()+facet_wrap(~Year)+labs(title="Web Revenue by Product 2017-2019",subtitle="Data Sourced From Vend",y="Revenue",x="Product")+theme(axis.text.x=element_blank(),axis.ticks.x=element_blank())

# Saved the plot as an rds into the graphics folder. Copied the plot from the graphics folder into the shiny app directory.

saveRDS(plot,file='Milestone-6/plot.rds')

# Explored a new dataframe, which examines revenue growth by product.

growth <- vend_data_2_years %>%
  group_by(Product) %>%
  mutate(oct2019='Oct 2019',oct2018='Oct 2018') %>%
  mutate(oct2019=as.numeric(oct2019),oct2018=as.numeric(oct2018)) 





# Created an interactive scatter plot, which looks at revenue by product for each of the three years of data. 

yearbyyear <- ggplot(vend_1,aes(x=Product, y=revenue, color=Year)) + geom_point() +  theme(axis.text.x = element_text(angle = 90, hjust = 1)) + labs(x="Product", y="Revenue")

# Stored the interactive plotly.

hover<-ggplotly(yearbyyear)

# Saved the plotly as an RDS file.

saveRDS(hover,file='Milestone-6/hover.rds')


```

In my plot, I decided to start examining Web Sales by product. Initially, I wanted to view this over time, but I realized that it would make more sense to facet the data since I was creating a column chart. While the data was already relatively clean, I ended up having to do more work than I had originally anticipated in order to make it work for the plot I had envisioned. The biggest step was remembering that I needed to use the gather function and then figuring out how to apply it in this case. After that, I also made sure I selected what I considered the most relevant products to be by arranging the data and selecting the top 10 products in terms of revenue. Lastly, I adjusted the aesthetics of the ploy as well in terms of the color, which pleased me aesthetically. 


```{r seasonal trends}

# Loaded all necessary libraries

library(tidyverse)
library(dplyr)
library(gganimate)
library(cowplot)
library(fs)
library(sf)
library(zoo)

# Examined web sales over time. Read in the CSV first.

web_over_time_2019 <- read.csv('Other_Data/Web over time.csv')

# Created a scatter plot examining net web sales by month. 

ggplot(web_over_time_2019,aes(x=month, y=net_sales))+geom_point()

# Created a variable called period in order to make sure the points ended up grouped properly when using transition states.

grouped_web_over_time_2019<- web_over_time_2019 %>%
  mutate(period=1)

# Created a plot examining 2019 net web sales by month using gganimate and transition states. Mutated so that month was properly formatted as a date. Styled the plot as well. 

time_2019_plot <- grouped_web_over_time_2019 %>%
  mutate(month=as.Date(as.yearmon(month))) %>%
  ggplot(aes(x=month, y=net_sales, color=month))+geom_point(size=3, aes(group=period))+transition_states(month) +     labs(title="2019 Web Sales by Month",x="Month", y="Net Sales") + shadow_mark()

# Saved the animation to the shiny app directory.

anim_save(filename='2019webtime',animation=time_2019_plot, path='Milestone-6')

# Created a plot also examining 2019 net web sales by month. Also properly formatted the month as a date. In this case, used a different animation to do a reveal creating a line as opposed to appearance and dissapearance. 

time_2019_plot_cooler<-grouped_web_over_time_2019 %>%
  mutate(month=as.Date(as.yearmon(month))) %>%
  ggplot(aes(x=month, y=net_sales, color=month))+geom_line()+geom_point(size=3, aes(group=period))+ coord_cartesian(clip = 'off') +transition_reveal(month) + labs(title='2019 Web Sales by Month',x="Month", y="Net Sales")

# Saved the plot to the shiny app directory.

anim_save(filename='2019webtimecool',time_2019_plot_cooler, path='Milestone-6')

# Created a variable called period in order to make sure the points ended up grouped properly when using transition states.

web_over_time_2018 <- read.csv('Other_Data/2018 web over time.csv') %>%
  mutate(period=1,year=2018)

# Created a plot examining 2018 net web sales by month using gganimate and transition states. Mutated so that month was properly formatted as a date. Styled the plot as well. 

time_2018_plot <- web_over_time_2018 %>%
  mutate(month=as.Date(as.yearmon(month))) %>%
  ggplot(aes(x=month, y=net_sales, color=month))+geom_point(size=3, aes(group=period))+transition_states(month) + labs(title="2018 Web Sales",x="Month", y="Net Sales")+shadow_trail()

# Saved the plot to the shiny app directory

anim_save(filename='2018webtime',animation=time_2018_plot, path='Milestone-6')

# Created a plot also examining 2018 net web sales by month. Also properly formatted the month as a date. In this case, used a different animation to do a reveal creating a line as opposed to appearance and dissapearance. 

time_2018_plot_cooler<-web_over_time_2018 %>%
  mutate(month=as.Date(as.yearmon(month))) %>%
  ggplot(aes(x=month, y=net_sales, color=month))+geom_line()+geom_point(size=3, aes(group=period))+ coord_cartesian(clip = 'off') +transition_reveal(month) + labs(title='2018 Web Sales by Month',x="Month", y="Net Sales")

anim_save(filename='2018webtimecooler',time_2018_plot_cooler, path='Milestone-6')









```

```{r}

# Read in web visits data

visit<-read.csv('Milestone-6/webvisits.csv')
```

```{r}

# Created a variable that indicates whether or not the user checked out. Made this "binomial." Filtered sessions to remove potential outliers.

purchase<-visit %>%
  mutate(total_checkouts=ifelse(total_checkouts>1,1,0)) %>%
  filter(total_sessions<60)

# Created a linear model examining the relationship between total sessions and checkouts. Made this model of family binomial.

lm(formula=total_checkouts~total_sessions, data=purchase, family="binomial")

# Created a scatter plot examining total sessions and whether a given customer checked out or not. Plotted a regression curve as well.

purchasers<-ggplot(purchase, aes(x=total_sessions, y=total_checkouts)) + geom_jitter(height=.1) + geom_smooth() + labs(x='Total Sessions', y='Checked Out')

# Saved the plot to the shiny app directory.

saveRDS(purchasers,file='Milestone-6/sessions.rds')

# Created a scatter plot examining the relationship between average duration and total pageviews. Styled the plot as well.

duration<- ggplot(purchase,(aes(x=avg_duration,y=total_pageviews))) + geom_jitter() + labs(title='Page Duration vs. Total Pageviews', x='Duration', y='Pageviews')

# Saved the plot as an RDS. Copied the file into the shiny app directory. 

saveRDS(duration,file='Milestone-6/duration')

```

```{r}
visit
library(stringr)
library(moderndive)

get_seconds <- function(x) {
    res <- as.numeric(str_match(x, "(\\d+).(\\d{1,2}\\.?\\d{0,2}).")[2:3])
    res[1]*60+res[2]
}
modifiedtime <- visit %>%
  mutate(format_duration=map(avg_duration,get_seconds)) %>%
  unnest(format_duration) %>%
  mutate(checked_out=ifelse(total_checkouts>=1,1,0)) %>%
  filter(format_duration>0) %>%
  filter(format_duration<500)

glm(formula=checked_out~format_duration,data=modifiedtime, family="binomial")
webmodel_duration<-modifiedtime %>%
  ggplot(aes(x=format_duration,y=checked_out))+geom_jitter(height=.1) + geom_smooth()

saveRDS(webmodel_duration,file='Milestone-6/webmodel_duration')


modifiedtime2 <- visit %>%
  mutate(format_duration=map(avg_duration,get_seconds)) %>%
  unnest(format_duration) %>%
  mutate(checked_out=ifelse(total_checkouts>=1,1,0)) %>%
  filter(format_duration>0) %>%
  filter(format_duration<150) 

glm(formula=checked_out~format_duration,data=modifiedtime2, family="binomial")
webmodel_duration_adjusted<-modifiedtime2 %>%
  ggplot(aes(x=format_duration,y=checked_out))+geom_jitter(height=.1) + geom_smooth()
webmodel_duration_adjusted

saveRDS(webmodel_duration_adjusted,file='Milestone-6/webmodel_duration_adjusted')
```

